<<<<<<< HEAD
---
title: "Data Management Group Assignment"
output: html_document
date: "2024-03-07"
editor_options: 
chunk_output_type: console
---
=======

>>>>>>> 61b49273c2c69a33c1fc130db359f453a1872bcf

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment=NA,attr.source='.numberLines')

rm(list=ls())
#install.packages("readr")
#install.packages("RSQLite")
#install.packages("dplyr")
install.packages("chron")
install.packages("ggplot2")
library(readr)
library(RSQLite)
library(dplyr)
library(chron)
library(ggplot2)
library(rmarkdown)
```

```{r connect}
my_connection <- RSQLite::dbConnect(RSQLite::SQLite(),"e-commerce.db")
                            
```

Create Category table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Category;
```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Category(
  category_id VARCHAR(20) PRIMARY KEY NOT NULL,
  category_name VARCHAR (20) NOT NULL,
  parent_id INT,
  parent_name VARCHAR (20)
  );
  
```

Create Customer table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Customer;
```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Customer(
  customer_id VARCHAR(50) PRIMARY KEY NOT NULL,
  email VARCHAR (100) NOT NULL,
  first_name VARCHAR (100) NOT NULL,
  last_name VARCHAR (100) NOT NULL,
  street_name VARCHAR (100) NOT NULL,
  post_code VARCHAR(64) NOT NULL,
  city VARCHAR (100) NOT NULL,
  password_c VARCHAR (10) NOT NULL, 
  phone_number INT (11) NOT NULL,
  referral_by VARCHAR(20)
  );
```

Create Supplier table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Supplier;
```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Supplier (
    seller_id VARCHAR(50) PRIMARY KEY NOT NULL,
    seller_store_name VARCHAR(100),
    supplier_email VARCHAR(255),
    password_s VARCHAR(255),
    receiving_bank VARCHAR(50),
    seller_rating INT,
    seller_phone_number VARCHAR(20),
    seller_address_street VARCHAR(255),
    s_post_code VARCHAR(50),
    s_city VARCHAR(50)
    );

```

Create Warehouse table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Warehouse;
```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Warehouse (
    warehouse_id VARCHAR(50) PRIMARY KEY NOT NULL,
    capacity INT,
    current_stock INT,
    w_city VARCHAR(50),
    w_post_code VARCHAR(50),
    w_address_street VARCHAR(255)
    );
```

Create Product table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Product;

```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Product (
  product_id INT PRIMARY KEY NOT NULL,
  product_name VARCHAR(50),
  category_id VARCHAR(20),
  warehouse_id VARCHAR(50),
  seller_id VARCHAR(50),
  product_weight FLOAT,
  product_price FLOAT,
  product_size VARCHAR(20),
  FOREIGN KEY (seller_id) REFERENCES Supplier(seller_id)
  FOREIGN KEY (category_id) REFERENCES Category(category_id),
  FOREIGN KEY (warehouse_id) REFERENCES Warehouse(warehouse_id)
  );
```

Create Shipment table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Shipment;

```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Shipment (
    shipment_id VARCHAR(50) PRIMARY KEY NOT NULL,
    shipping_method VARCHAR(50),
    shipping_charge FLOAT
    );
```

Create Orders table

```{sql connection=my_connection}
DROP TABLE IF EXISTS Orders;
```

```{sql connection=my_connection}
CREATE TABLE IF NOT EXISTS Orders (
    order_id VARCHAR(50) NOT NULL,
    order_date DATE NOT NULL,
    order_status VARCHAR(50),
    quantity_of_product_ordered INT,
    payment_method VARCHAR(50),
    voucher_value INT,
    review_rating INT,
    shipment_id VARCHAR(50),
    product_id VARCHAR(50) NOT NULL,
    customer_id VARCHAR(50) NOT NULL,
    PRIMARY KEY (order_id, customer_id, product_id),

    FOREIGN KEY (shipment_id) REFERENCES Shipment(shipment_id),
    FOREIGN KEY (customer_id) REFERENCES Customer(customer_id),
    FOREIGN KEY (product_id) REFERENCES Product(product_id)
    );
    
```
<<<<<<< HEAD


Read .csv files in (old data)

```{r dataloading,message=FALSE,warning=FALSE}
Category <- readr::read_csv("/cloud/project/old_data/category_data.csv")
Category$category_id <- as.character(Category$category_id)
Category$parent_id <- as.character(Category$parent_id)


Customer <- readr::read_csv("/cloud/project/old_data/customer_data.csv")
Customer$customer_id <- as.character(Customer$customer_id)


Supplier <- readr::read_csv("/cloud/project/old_data/supplier_data.csv")
Supplier$seller_id <- as.character(Supplier$seller_id)


Warehouse <- readr::read_csv("/cloud/project/old_data/warehouse_data.csv")
Warehouse$warehouse_id <- as.character(Warehouse$warehouse_id)


Product <- readr::read_csv("/cloud/project/old_data/product_data.csv")
Product$product_id <- as.character(Product$product_id)
Product$seller_id <- as.character(Product$seller_id)
Product$warehouse_id <- as.character(Product$warehouse_id)
Product$category_id <- as.character(Product$category_id)


Shipment <- readr::read_csv("/cloud/project/old_data/shipment_data.csv")
Shipment$shipment_id <- as.character(Shipment$shipment_id)


Orders <- readr::read_csv("/cloud/project/old_data/order_data.csv")

Orders$order_date <- as.Date(Orders$order_date, format = "%Y/%m/%d")
Orders$order_date <- as.character(Orders$order_date)
Orders$order_id <- as.character(Orders$order_id)
Orders$customer_id <- as.character(Orders$customer_id)
Orders$product_id <- as.character(Orders$product_id)
Orders$shipment_id <- as.character(Orders$shipment_id)

#db exucute query

```

Write them to the database

```{r writebacktodb}
RSQLite::dbWriteTable(my_connection,"Category",Category,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Customer",Customer,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Supplier",Supplier,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Warehouse",Warehouse,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Product",Product,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Shipment",Shipment,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Orders",Orders,append=TRUE)

```

Use this to verify the table we created

```{sql connection=my_connection}
PRAGMA table_info(Orders);
```


Read .csv files in (new data)

```{r newdataloading,message=FALSE,warning=FALSE}
Category_new <- readr::read_csv("/cloud/project/new_data/category_data_new.csv")
Category_new$category_id <- as.character(Category_new$category_id)
Category_new$parent_id <- as.character(Category_new$parent_id)


Customer_new <- readr::read_csv("/cloud/project/new_data/customer_data_new.csv")
Customer_new$customer_id <- as.character(Customer_new$customer_id)


Supplier_new <- readr::read_csv("/cloud/project/new_data/supplier_data_new.csv")
Supplier_new$seller_id <- as.character(Supplier_new$seller_id)


Warehouse_new <- readr::read_csv("/cloud/project/new_data/warehouse_data_new.csv")
Warehouse_new$warehouse_id <- as.character(Warehouse_new$warehouse_id)


Product_new <- readr::read_csv("/cloud/project/new_data/product_data_new.csv")
Product_new$product_id <- as.character(Product_new$product_id)
Product_new$seller_id <- as.character(Product_new$seller_id)
Product_new$warehouse_id <- as.character(Product_new$warehouse_id)
Product_new$category_id <- as.character(Product_new$category_id)


Shipment_new <- readr::read_csv("/cloud/project/new_data/shipment_data_new.csv")
Shipment_new$shipment_id <- as.character(Shipment_new$shipment_id)


Orders_new <- readr::read_csv("/cloud/project/new_data/order_data_new.csv")

Orders_new$order_date <- as.Date(Orders_new$order_date, format = "%Y/%m/%d")
Orders_new$order_date <- as.character(Orders_new$order_date)
Orders_new$order_id <- as.character(Orders_new$order_id)
Orders_new$customer_id <- as.character(Orders_new$customer_id)
Orders_new$product_id <- as.character(Orders_new$product_id)
Orders_new$shipment_id <- as.character(Orders_new$shipment_id)

#db exucute query

```

Append new data to the database

```{r writebacktodbnew}
RSQLite::dbWriteTable(my_connection,"Category",Category_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Customer",Customer_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Supplier",Supplier_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Warehouse",Warehouse_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Product",Product_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Shipment",Shipment_new,append=TRUE)
RSQLite::dbWriteTable(my_connection,"Orders",Orders_new,append=TRUE)
```

Append new data to the current tables for visualization in r
```{r}
Warehouse <- rbind(Warehouse, Warehouse_new)
Product <- rbind(Product, Product_new)
Customer <- rbind(Customer, Customer_new)
Category <- rbind(Category, Category_new)
Supplier <- rbind(Supplier, Supplier_new)
Orders <- rbind(Orders, Orders_new)
Shipment <- rbind(Shipment, Shipment_new)

```



```{sql connection=my_connection}
SELECT * FROM Orders

```


```{sql connection=my_connection}
SELECT * FROM Category
LIMIT 10

```
Data analysis and visualization

Rank order value from highest to lowest

```{sql connection=my_connection}
SELECT 
    o.order_id,
    o.customer_id,
    SUM(o.quantity_of_product_ordered * (p.product_price - o.voucher_value)) AS total_value
FROM 
    Orders o
JOIN 
    Product p ON o.product_id = p.product_id
GROUP BY 
    o.order_id
ORDER BY 
    total_value DESC;
```

Warehouse capacity v.s. current stock level

```{r barplot}
barplot(Warehouse$capacity, col = "steelblue", ylim = c(0, max(Warehouse$capacity, Warehouse$current_stock)),
        main = "Warehouse Capacity and Current Stock", xlab = "Warehouse ID", ylab = "Quantity")
barplot(Warehouse$current_stock, col = "lightpink", add = TRUE)
legend("topright", legend = c("Capacity", "Current Stock"), fill = c("steelblue", "lightpink"))
```


=======
>>>>>>> 61b49273c2c69a33c1fc130db359f453a1872bcf
